First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-06-08 eg6-letters/NIM/author_list.tex
Add author
Various fixes for NIM and coherent letter

\author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{N.~Baltzell}  \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
\author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{E.~Voutier} \affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
%\author{} \affiliation{}
%

>>>>

\author{R.~Dupr\'e} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{M.~Hattawy} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\author{N.~Baltzell} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{H.~Fenker} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
\author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{E.~Voutier} \affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
%\author{} \affiliation{}
%

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
add Kim's acknowledgment
Various fixes for NIM and coherent letter

Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu$ is the energy of the virtual photon, and 
$M_N$ is the nucleon mass. $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally in DVCS. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ a GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target form factors, which are well known in this
kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
measure. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the squares of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
for a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Explicit expressions of the kinematic factors $\alpha_i$ are derived in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

>>>>

Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable 
$x_{A}$: $\xi\approx {{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, 
$\nu$ is the energy of the virtual photon, and 
$M_A$ is the nuclei mass. $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally in DVCS. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ a GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target form factors, which are well known in this
kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
measure. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the squares of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
for a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Explicit expressions of the kinematic factors $\alpha_i$ are derived 
from expressions in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

Kim- The National Research Foundation of Korea
